Clause size reduction with all-UIP Learning

### 2020-02-18 paper.tex
fix new figure link
add cites info
fix typos

\subsubsection{Clause Reduction with $\allUip$}
To precisely measure $\allUip$ clause reduction power, we compare each instance's learnt clause size from $\allUipMin$ and $\allUipPure$ against 1-UIP. Fig.~\ref{fig:len_pdf} shows the probability density distribution (PDF) of the relative clause size of $\allUip$ learning
schemes ($\allUipMin$ in green and $\allUipPure$ in red) for each instance. $\allUipMin$ ($\allUipPure$ resp.) produces shorter clauses for 88.5\% (77.7\%) of instances, and the average relative reduction rate from 1-UIP is 18.6\% (16.7\%). Fig.~\ref{fig:len_compare} compares the absolute clause size of $\allUipMin$, $\allUipPure$ and 1-UIP per instance.  
Both $\allUip$ schemes generally yield smaller clauses,
and the size reduction is more significant for instances with larger 1-UIP clause size.

@@

  \begin{minipage}[t]{0.5\textwidth}
   \includegraphics[width=\textwidth]{figures/clause_reduction_PDF}
   \caption{Relative clause size reduction distribution. X axis
      indicates the relative size of difference between i-uip and
      1-uip clauses (calculated as
      $\dfrac{|C_1|-|C_i|}{|C_1|}$ ) for
      each instance, and Y axis shows the probability density.}
       \label{fig:len_pdf}
  \end{minipage}
  & &
  \begin{minipage}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/i-uip-sizes-compare.pdf}
    \caption{Average clause size comparison plot. Each point in the
      plot represents an instance. X and Y axis shows the clause
      length from $\allUip$ and 1-UIP, respectively. Each green (red)
      dot represents an compared instance between $\MapleBase$ and
      $\MapleIUIMin$ ($\allUipPure$).}
      \label{fig:len_compare}
  \end{minipage}

@@

On the SAT 2019 race winner $\MapleNineShort$,  three out of four$\allUip$ configurations solved instances 6, 5 and 5 more instances than 1-UIP, respectively. The solver uses duplicate learning (DL) to prioritize clauses that are learned multiple times. We observed that $\allUip$ configurations
i-UIP clauses are less likely to be duplicated. As an example, $\allUipMin$ in average, added 12\% less duplicated clauses into the
core clause database than 1-UIP. This observation is surprising and the cause is unclear.

>>>>

\subsubsection{Clause Reduction with $\allUip$}
To precisely measure $\allUip$ clause reduction power, we compare each instance's learnt clause size from $\allUipMin$ and $\allUipPure$ against 1-UIP. Fig.~\ref{fig:len_pdf} shows the probability density distribution (PDF) of the relative clause size of $\allUip$ learning
schemes ($\allUipMin$ in green and $\allUipPure$ in red) for each instance. $\allUipMin$ ($\allUipPure$ resp.) produces shorter clauses for 88.5\% (77.7\%) of instances, and the average relative reduction ratio over 1-UIP is 18.6\% (16.7\%). Fig.~\ref{fig:len_compare} compares the absolute clause size of $\allUipMin$, $\allUipPure$ and 1-UIP per instance.  
Both $\allUip$ schemes generally yield smaller clauses,
and the size reduction is more significant for instances with larger 1-UIP clause.

@@

  \begin{minipage}[t]{0.5\textwidth}
   \includegraphics[width=\textwidth]{figures/clause_reduction_PDF.pdf}
   \caption{Relative clause size reduction distribution. X axis
      indicates the relative size of difference between i-uip and
      1-uip clauses (calculated as
      $\dfrac{|C_1|-|C_i|}{|C_1|}$ ) for
      each instance, and Y axis shows the probability density.}
       \label{fig:len_pdf}
  \end{minipage}
  & &
  \begin{minipage}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/clause_size_compare.pdf}
    \caption{Average clause size comparison plot. Each point in the
      plot represents an instance. X and Y axis shows the clause
      length from $\allUip$ and 1-UIP, respectively. Each green (red)
      dot represents an compared instance between $\MapleBase$ and
      $\MapleIUIMin$ ($\allUipPure$).}
      \label{fig:len_compare}
  \end{minipage}

@@

On the SAT 2019 race winner $\MapleNineShort$,  three out of four$\allUip$ configurations solved instances 6, 5 and 5 more instances than 1-UIP, respectively. The solver uses duplicate learning (DL) to prioritize clauses that are learned multiple times. We observed that clauses learnt from $\allUip$ configurations are less likely to be duplicated. As an example, $\allUipMin$ in average, added 12\% less duplicated clauses into the
core clause database than 1-UIP. This observation is surprising, and the cause is unclear.
